Supplementary Information

### 2015-07-01 manuscript/supplement.tex
lets have some line numbers here too

\title{Supplementary Information}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2, Canada\\
\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\}

@@

\vspace{0.4 in}
\beginsupplement
% \begin{landscape}
\subsection*{Appendix S1: Details of Food Web Sources and Selection}

  We combined published food webs from~\citet{GlobaWeb},~\citet{Riede2011},
  and~\citet{Dunne2013}. Of the 358 food webs available
  from~\citet{Globalweb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalized
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\citet{GlobalWeb}.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used
  to assess the roles of parasites within food webs. As all but 3 of the webs
  from~\citet{GlobalWeb} contained only free-living species, we removed the
  the parasites (and all interactions involving them) from these webs (and the
  3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living
  species only. In addition, we included 30 of the 40 webs
  from~\citet{Riede2011}, which were originally collected to test the
  relationship between consumer and resources body sizes. Nine of the
  remaining webs in the~\citet{Riede2011} dataset were also included in
  the~\citet{GlobalWeb}  dataset, and the last web was derived from an
  unpublished source. This gave us a database of 263 webs. As we wished to use
  the logarithmic form of power-law relationships, we then eliminated any food
  web which did not have at least one each of basal resources, intermediate
  consumers, and top predators (to obtain  non-zero proportions of each
  category). Our final sample size was thereby reduced to 196 food webs.

@@

 See Table S1 for a list of rejected webs and reasons for their
  exclusion.

\subsection*{Appendix S2: Supplemental Methods and Results - scaling Relationships with S}

>>>>

\title{Supplementary Information}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
\date{\footnotesize$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2, Canada\\
\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\}

@@

\vspace{0.4 in}
\beginsupplement
\linenumbers
% \begin{landscape}
\subsection*{Appendix S1: Details of Food Web Sources and Selection}

  We combined published food webs from~\citet{GlobalWeb},~\citet{Riede2011},
  and~\citet{Dunne2013}. Of the 358 food webs available
  from~\citet{GlobalWeb}, 59 were rejected because their original source was
  unpublished or could not be retrieved. We further eliminated 13 source or
  sink webs (which describe feeding links flowing from or to a particular
  resource or top predator rather than the interactions of an entire
  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
  describing competitive interactions. Finally, we eliminated 2 webs
  describing  inferred interactions in an extinct community, 10 ``generalized
  schemes'' that were not based on direct field data, and 4 webs where it was
  not clear which of several described study sites were used to construct the
  food web (and therefore the latitude of the food web could not be
  included). This left us with 226 webs from~\citet{GlobalWeb}.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used
  to assess the roles of parasites within food webs. As all but 3 of the webs
  from~\citet{GlobalWeb} contained only free-living species, we removed the
  the parasites (and all interactions involving them) from these webs (and the
  3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living
  species only. In addition, we included 30 of the 40 webs
  from~\citet{Riede2011}. Nine of the
  remaining webs in the~\citet{Riede2011} dataset were also included in
  the~\citet{GlobalWeb}  dataset, and the last web was derived from an
  unpublished source. This gave us a database of 263 webs. As we wished to use
  the logarithmic form of power-law relationships, we then eliminated any food
  web which did not have at least one each of basal resources, intermediate
  consumers, and top predators (to obtain  non-zero proportions of each
  category). Our final sample size was thereby reduced to 196 food webs.

@@

 See Table~\ref{S1} for a list of rejected webs and reasons for their
  exclusion.

  \newpage
  \begin{landscape}

    \begin{table}[h!]
    \centering
    \caption{Sources of food webs considered for use in this study. ``Collection" indicates the direct source of the
    food web (i.e., where the interaction matrix was obtained) while ``Original source" indicates the original publication
    of the food web. We also show the ecosystem type, country of origin, and latitude for each food web, as well as whether
    it was ultimately included in the study. Collection 1 is~\citet{Riede2011}, collection 2 is~\citet{Dunne2013}, and collection 3 is~\citet{GlobalWeb}.}
    \label{S1}

    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection \\
        \hline
        Alamitos & 1 & \citet{Harrison1995}    & stream & 37,12,25 N & Yes   &       \\
        Alford & 1 & \citet{Havens1992}    & lake  & 44,15,41.59 N & Yes   &       \\
        Beaver & 1 & \citet{Havens1992}    & lake  & 44,18,58.13 N & Yes   &       \\
        Bere  & 1 & \citet{Woodward2008}  & stream & 50,45,7 N & Yes   &       \\
        Bridge & 1 & \citet{Havens1992}    & lake  & 44,09,42.66 N & Yes   &       \\
        Broad & 1 & \citet{Townsend1998}  & stream & 45.896938 S & Yes   &       \\
        Broadstone & 1 & \citet{Woodward2005} & stream  & 51,01,05 N & Yes   &       \\
        Calero & 1 & \citet{Harrison1995}    & stream & 37,11,09 - 20 N & Yes   &       \\
        Canton & 1 & \citet{Townsend1998}  & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) \\
        Carpinteria2006 & 1 & \citet{Lafferty2006}    & estuary & 34.41 - 34.40 N & Yes   &       \\
        Chub  & 1 & \citet{Havens1992}    & lake  & 43,31,39.36 N & Yes   &       \\
        Coachella & 1 & \citet{Polis1991a} & terrestrial & 33,54 N & Yes   &       \\
        Connery & 1 & \citet{Havens1992}    & lake  & 44,18,42.10 N & Yes   &       \\
        Corte & 1 & \citet{Harrison1995}    & stream & 37,56,28 - 37,57,39 N & Yes   &       \\
        Coyote & 1 & \citet{Harrison1995}    & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       \\
        German & 1 & \citet{Townsend1998}  & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) \\
        GrandeCl & 1 & \citet{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
        GrandeSc & 1 & \citet{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
        Guadalupe & 1 & \citet{Harrison1995}    & stream & 37,27,54 - 37,21,17 N & Yes   &       \\
        Hainich   & 1 & Unpublished  & terrestrial &       & No    & Could not locate original source \\
        LittleKyeBurn & 1 & \citet{Townsend1998}  & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) \\
        LittleRock & 1 & \citet{Martinez1991}    & lake  & 45,44,07.94 N & Yes   &       \\
        Mondego & 1 & \citet{Patricio2006}  & estuary & 40,08 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        Montane Forest & 1 & \citet{Rasmussen1941}    & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) \\
        Reef  & 1 & \citet{Opitz1996}  & marine & 18,29 - 17,53 N & Yes   &       \\
        Sierra & 1 & \citet{Brose2005}    & lake  & 36,50 - 37,02 N & Yes   &       \\
        SimberloffE1 & 1 & \citet{Simberloff1976}  & terrestrial & 24,40,37.29 N & Yes   &       \\
        SimberloffE2 & 1 & \citet{Simberloff1976}  & terrestrial & 24,40,33 N & Yes   &       \\
        SimberloffE3 & 1 & \citet{Simberloff1976}  & terrestrial & 24,41,23.82 N & Yes   &       \\
        SimberloffE7 & 1 & \citet{Simberloff1976}  & terrestrial & 25,15 N & Yes   &       \\
        SimberloffE9 & 1 & \citet{Simberloff1976}  & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       \\
        SimberloffST2 & 1 & \citet{Simberloff1976}  & terrestrial & 24,36,16 N & Yes   &       \\
        Skipwith & 1 & \citet{Warren1989}  & lake  & 53,40 N & Yes   &       \\
        Stink & 1 & \citet{Havens1992}    & lake  & 43,37,55.88 N & Yes   &       \\
        StMarks & 1 & \citet{Christian1999}    & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) \\
        Stony  & 1 & \citet{Townsend1998}  & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) \\
        TreleaseWoods & 1 & \citet{Twomey1945}    & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) \\
        Tuesday & 1 & \citet{Jonsson2005}    & lake  & 46,13 N & Yes   &       \\
        Weddell Sea & 1 & \citet{Brose2005}  & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) \\
        Ythan & 1 & \citet{Huxham1996}     & marine &       & No    & Duplicated in Dunne (YthanDunne) \\
        BahiaDunne & 2 & \citet{Hechinger2011}  & estuary & 30.43 - 30.46 N & Yes   &        \\
        CarpinteriaDunne & 2 & \citet{Hechinger2011}    & estuary & 34.41 - 34.40 N & Yes   &        \\
        EsteroDunne & 2 & \citet{Hechinger2011}  & estuary & 31.78 - 31.69 N & Yes   &        \\
        FjordDunne & 2 & \citet{Zander2011}  & estuary & 54.92 - 54.75 N & Yes   &        \\
        OtagoDunne & 2 & \citet{Mouritsen2011}  & estuary & 45.78 - 45.88 S & Yes   &        \\
        SyltDunne & 2 & \citet{Thieltges2011}  & estuary & 54.83 - 55.12 N & Yes   &        \\
        YthanDunne & 2 & \citet{Huxham1996}  & estuary & 57,18,32 N & Yes   &        \\
        1     & 3 & \citet{Qazim1970}  & estuary &       & No    & Could not locate original source \\
        2     & 3 & \citet{Day1967} & estuary &       & No    & Could not locate original source \\
        3     & 3 & \citet{Woodwell1967}    & estuary & 41,03,11 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        4     & 3 & \citet{Johnston1956}    & estuary &       & No    & Sink web \\
        5     & 3 & \citet{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
        6     & 3 & \citet{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
        7     & 3 & \citet{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
        8     & 3 & \citet{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
        9     & 3 & \citet{Kitching1967}  & stream &       & No    & Could not locate original source \\
        10    & 3 & \citet{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        11    & 3 & \citet{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        12    & 3 & \citet{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        13    & 3 & \citet{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        14    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        15    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        16    & 3 & \citet{Copeland1974}    & estuary &       & No    & Could not locate original source \\
        17    & 3 & \citet{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalized scheme \\
        18    & 3 & \citet{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
        19    & 3 & \citet{Brooks1963}    & lake &       & No    & Could not locate original source \\
        20    & 3 & \citet{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
        21    & 3 & \citet{Patten1979}  & marine & 70-85 S & Yes   &       \\
        22    & 3 & \citet{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
        23    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        24    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        25    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        26    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        27    & 3 & \citet{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
        28    & 3 & \citet{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
        29    & 3 & \citet{Dunbar1953}  & marine &       & No    & Generalized scheme \\
        30    & 3 & \citet{Mackintosh1964}  & marine &       & No    & Generalized scheme \\
        31    & 3 & \citet{Petipa1970}  & marine &       & No    & Could not locate original source \\
      \hline
      \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        32    & 3 & \citet{Petipa1970}  & marine &       & No    & Could not locate original source \\
        33    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        34    & 3 & \citet{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
        35    & 3 & \citet{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
        36    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        37    & 3 & \citet{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
        38    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        39    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        40    & 3 & \citet{Harrison1962}  & terrestrial &       & No    & Generalized scheme \\
        41    & 3 & \citet{Parin1970}  & marine &       & No    & Could not locate original source \\
        42    & 3 & \citet{Vinogradov1978}  & marine &       & No    & Study site unclear \\
        43    & 3 & \citet{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
        44    & 3 & \citet{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        45    & 3 & \citet{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
        46    & 3 & \citet{Patten1975}    & lake & 33,54 N & Yes   &       \\
        47    & 3 & \citet{Harris1980}    & lake &       & No    & Study site unclear \\
        48    & 3 & \citet{Simenstad1978}    & marine &       & No    & Extinct species \\
        49    & 3 & \citet{Simenstad1978}    & marine &       & No    & Extinct species \\
        50    & 3 & \citet{Nybakken1982}    & marine &       & No    & Generalized scheme \\
        51    & 3 & \citet{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
        52    & 3 & \citet{Paine1980a}    & marine & 58,27 N & Yes   &       \\
        53    & 3 & \citet{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
        55    & 3 & \citet{Milne1972}  & estuary &       & No    & Could not locate original source \\
        56    & 3 & \citet{Milne1972}  & estuary &       & No    & Could not locate original source \\
        57    & 3 & \citet{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        58    & 3 & \citet{Cohen1990}  & lake & 51,46 N & Yes   &       \\
        59    & 3 & \citet{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
        60    & 3 & \citet{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
        61    & 3 & \citet{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        62    & 3 & \citet{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        63    & 3 & \citet{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
        64    & 3 & \citet{Cummins1966}    & stream & 41,39,33 N & Yes   &       \\
        65    & 3 & \citet{Tsuda1972}  & stream & 34,21,20 - 34,23,21 N & Yes   &       \\
        66    & 3 & \citet{Mann1972a}  & stream & 51,30 N & Yes   &       \\
        67    & 3 & \citet{Carlson1968}    & stream & 40,24,16 N & Yes   &       \\
        68    & 3 & \citet{Morgan1972}  & lake &       & No    & Could not locate original source \\
        69    & 3 & \citet{Cohen1990}  & estuary &       & No    & Could not locate original source \\
        70    & 3 & \citet{Kemp1977}    & estuary & 28,54,08 N & Yes   &       \\
        71    & 3 & \citet{Sorokin1972}  & lake & 48,00 N & Yes   &       \\
        72    & 3 & \citet{Baril1983}  & lake & 46,02 N & Yes   &       \\
        73    & 3 & \citet{Schiemer1979}  & lake &       & No    & Could not locate original source \\
        74    & 3 & \citet{Cohen1990} & marine & 34,15,00 S & Yes   &       \\
        75    & 3 & \citet{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
        76    & 3 & \citet{Schiemer1979}  & lake & 47,42 - 47,54 N & Yes   &       \\
        77    & 3 & \citet{Cohen1990}  & lake &       & No    & Could not locate original source \\
        78    & 3 & \citet{Burgis1972}  & lake & 0     & Yes   &       \\
        79    & 3 & \citet{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        80    & 3 & \citet{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        81    & 3 & \citet{Hatanaka1977}  & marine &       & No    & Could not locate original source \\
        82    & 3 & \citet{Cohen1990} & marine &       & No    & Could not locate original source \\
        83    & 3 & \citet{Cohen1990}  & lake &       & No    & Could not locate original source \\
        84    & 3 & \citet{Wilbur1972}    & lake & 42,28,42 N & Yes   &       \\
        85    & 3 & \citet{Mizuno1982}  & lake &       & No    & Could not locate original source \\
        86    & 3 & \citet{Hogetsu1979}  & marine & 34,36 - 35,38 N & Yes   &       \\
        87    & 3 & \citet{Bradstreet1982}  & terrestrial & 72,46,34.95 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        88    & 3 & \citet{Kuusela1980}  & stream &       & No    & Could not locate original source \\
        89    & 3 & \citet{Hartley1948}  & stream & 52,13 N & Yes   &       \\
        91    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        92    & 3 & \citet{Swan1961}  & terrestrial &       & No    & Generalized scheme \\
        93    & 3 & \citet{Pattie1966}    & terrestrial & 45 N  & Yes   &       \\
        94    & 3 & \citet{Brown1971}    & terrestrial &       & No    & Could not locate original source \\
        95    & 3 & \citet{Brown1975}    & terrestrial & 70,11,14.18 N & Yes   &       \\
        96    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        97    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        98    & 3 & \citet{Holm1980}  & terrestrial &       & No    & Could not locate original source \\
        99    & 3 & \citet{Howes1954}    & terrestrial & 32,36 N & Yes   &       \\
        100   & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
        101   & 3 & \citet{Cohen1990} & lake  &       & No    & Could not locate original source \\
        102   & 3 & \citet{Shushkina1979}  & marine & 10 S - 15 N & Yes   &       \\
        103   & 3 & \citet{Petipa1979}  & marine &       & No    & Generalized scheme \\
        104   & 3 & \citet{Menge1976}  & marine & 4,48,04 N & Yes   &       \\
        105   & 3 & \citet{Edwards1982}  & marine & 42,40 N & Yes   &       \\
        106   & 3 & \citet{Glynn1965}  & marine &       & No    & Could not locate original source \\
        107   & 3 & \citet{Peterson1979}  & marine & 39,52,02 N & Yes   &       \\
        108   & 3 & \citet{Hewatt1937}  & marine & 36,37 N & Yes   &       \\
        109   & 3 & \citet{Castilla1981} & marine &       & No    & Could not locate original source \\
        110   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        111   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        112   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        113   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
        114   & 3 & \citet{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        115   & 3 & \citet{Koepcke1952}  & marine &       & No    & Could not locate original source \\
        116   & 3 & \citet{Hurlbert1972}  & lake  & 35,09,19 S & Yes   &       \\
        117   & 3 & \citet{Zaret1973}  & lake  & 9,11,31.50 N & Yes   &       \\
        118   & 3 & \citet{Bindloss1972}  & lake  & 56,41,18.71 N & Yes   &       \\
        119   & 3 & \citet{Mann1972}  & stream & 51,27 N & Yes   &       \\
        120   & 3 & \citet{Moriarty1973}  & lake  & 0,00,58 N & Yes   &       \\
        121   & 3 & \citet{VanEs1977}  & estuary & 53,20 - 53,15 N & Yes   &       \\
        122   & 3 & \citet{Nixon1973}  & estuary & 41,33,04 N & Yes   &       \\
        123   & 3 & \citet{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
        124   & 3 & \citet{Collins1976}  & stream & 44,34 N & Yes   &       \\
        125   & 3 & \citet{Landry1977}  & marine &       & No    & Generalized scheme \\
        126   & 3 & \citet{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
        127   & 3 & \citet{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        128   & 3 & \citet{Beaver1979}  & lake  &       & No    & Could not locate original source \\
        129   & 3 & Unpublished & terrestrial &       & No    & Unpublished \\
        130   & 3 & \citet{Odum1975}  & estuary & 27,12 N & Yes   &       \\
        131   & 3 & \citet{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        132   & 3 & \citet{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
        133   & 3 & \citet{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
        134   & 3 & \citet{Beaver1985}  & lake  & 19 S  & Yes   &       \\
        135   & 3 & \citet{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
        136   & 3 & \citet{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
        137   & 3 & \citet{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
        138   & 3 & \citet{Kitching1983}     & lake  &       & No    & Could not locate original source \\
        139   & 3 & \citet{Kitching1983}  & lake  &       & No    & Could not locate original source \\
        140   & 3 & \citet{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
        141   & 3 & \citet{Seifert1976}  & terrestrial &       & No    & Competition network \\
        142   & 3 & \citet{Seifert1976}  & terrestrial &       & No    & Competition network \\
        143   & 3 & \citet{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
         \hline
      \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        144   & 3 & \citet{Snow1958}  & lake  &       & No    & Could not locate original source \\
        145   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        146   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        147   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        148   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
        149   & 3 & \citet{Force1974}    & terrestrial &       & No    & Host-parasitoid web \\
        150   & 3 & \citet{Hopkins1984}     & terrestrial &       & No    & Host-parasitoid web \\
        151   & 3 & \citet{Richards1926}     & terrestrial & 51,20,04 N & Yes   &       \\
        152   & 3 & \citet{Whittaker1984}    & terrestrial &       & No    & Source web \\
        153   & 3 & \citet{Mayse1978}    & terrestrial & 40,06,38 N & Yes   &       \\
        154   & 3 & \citet{Mayse1978}    & terrestrial & 39,56,41 N & Yes   &       \\
        155   & 3 & \citet{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
        156   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        157   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        158   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        159   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        160   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        161   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        162   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        163   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        164   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        165   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        166   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        167   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
        168   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        169   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\        
        170   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        171   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\      
        172   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        173   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        174   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        175   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        176   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        177   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        178   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
        \hline
        \end{tabular}}%
      \end{table}

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        179   & 3 & \citet{Robinson1953}  & terrestrial &       & No    & Source web \\
        180   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
        181   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
        182   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
        183   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
        184   & 3 & \citet{Beaver1972}     & terrestrial &       & No    & Could not locate original source \\
        185   & 3 & \citet{Chapman1955}     & terrestrial &       & No    & Source web \\
        186   & 3 & \citet{Cornaby1974}  & terrestrial &       & No    & Source web \\
        187   & 3 & \citet{Cornaby1974}  & terrestrial &       & No    & Source web \\
        188   & 3 & \citet{Jiron1981}  & terrestrial &       & No    & Source web \\
        189   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
        190   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
        191   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
        192   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
        193   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
        194   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
        195   & 3 & \citet{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
        196   & 3 & \citet{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
        197   & 3 & \citet{Mohr1943}    & terrestrial &       & No    & Source web \\
        198   & 3 & \citet{Schoenly1983}  & terrestrial &       & No    & Source web \\
        199   & 3 & \citet{Valiela1969}    & terrestrial &       & No    & Source web \\
        200   & 3 & \citet{Valiela1974}    & terrestrial &       & No    & Source web \\
        201   & 3 & \citet{Valiela1974}    & terrestrial &       & No    & Source web \\
        202   & 3 & \citet{Allan1982}    & stream & 38,50,21 N & Yes   &       \\
        203   & 3 & \citet{Collins1976}    & stream & 44,24 N & Yes   &       \\
        204   & 3 & \citet{Fryer1959} & lake  & 11,36,39 S & Yes   &       \\
        205   & 3 & \citet{Hildrew1985}     & stream & 51,01,05 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}
